Assessment of referee comment regarding q value and zero assumption

### 2016-12-09 analysis/investigate_hu_badcoverage.Rmd
update
Rendered referee_uaza.html and fixed chunk-options label to chunk_options.

```{r chunk-options, include=FALSE}
source("chunk-options.R")
```

@@

```{r}
  eg=load_example(dsc_shrink,42,"flat-top",method="ash.hu.s","../code/dsc-shrink")
  eg$output$fitted.g
```

>>>>

```{r chunk_options, include=FALSE}
source("chunk-options.R")
```

@@

```{r}
  eg=load_example(dsc_shrink,42,"flat-top",method="ash.hu.s","../code/dsc-shrink")
  eg$output$fitted_g
```

### 2016-12-09 analysis/make_GOODPOOR_figs.Rmd
Rendered referee_uaza.html and fixed chunk-options label to chunk_options.

```{r chunk-options, include=FALSE}
library(ashr)
library(qvalue)
library(locfdr)
library(mixfdr)
library(ggplot2)
source("chunk-options.R")
source("../R/plot_FDReg_hist.R")
```

>>>>

```{r chunk_options, include=FALSE}
library(ashr)
library(qvalue)
library(locfdr)
library(mixfdr)
library(ggplot2)
source("chunk-options.R")
source("../R/plot_FDReg_hist.R")
```

### 2016-12-09 analysis/referee_uaza.Rmd
Revised	efron.fcr.Rmd.
Rendered referee_uaza.html and fixed chunk-options label to chunk_options.

```{r chunk-options, include=FALSE}
source("chunk-options.R")
```

# Simulation

A referee reported a simulation of 10,000 hypotheses, a fraction 0.8 are null ($\mu_i=0$), and a fraction 0.2 are alternative with effect $\mu_i \sim N(0,1)$. For each effect $i$ there
are n=30 observations from $x_{i,j} \sim N(\mu_i,1)$ and a one-sample t test is used to compute a $p$ value. The referee correctly notes that these simulations i) obey the
unimodal assumption (UA), and ii) have the property that "most" $z$ scores near 0 are null (Efron's "Zero Assumption"; ZA).
The motivation is to demonstrate that the UA and the ZA are not contradictory.

@@

```{r}
set.seed(100)
mu = c(rep(0,8000),rnorm(2000))
x = matrix(rnorm(30*10000),nrow=10000,ncol=30)+mu
ttest.pval = function(x){return(t.test(x)$p.value)}
x.p = apply(x,1,ttest.pval)
```

@@

# Explanation

>>>>

A referee reported a simulation of 10,000 hypotheses, a fraction 0.8 are null ($\mu_i = 0$), and a fraction 0.2 are alternative with effect $\mu_i \sim 
N(0,1)$. For each effect $i$ there are n=30 observations from $x_{i,j} \sim N(\mu_i,1)$ and a one-sample t test is used to compute a $p$ value. The 
referee correctly notes that these simulations i) obey the unimodal 
assumption (UA), and ii) have the property that "most" $z$ scores near 0 are 
null (Efron's "Zero Assumption"; ZA). The motivation is to demonstrate that 
the UA and the ZA are not contradictory.

@@

First, we load the necessary libraries, and specify settings for displaying 
the plots in the rendered document.

```{r chunk_options, include=FALSE}
source("chunk-options.R")
```

## Simulation

First, we generate a small data set.

```{r sim_data}
set.seed(100)
mu = c(rep(0,8000),rnorm(2000))
x = matrix(rnorm(30*10000),nrow=10000,ncol=30)+mu
ttest.pval = function(x){return(t.test(x)$p.value)}
x.p = apply(x,1,ttest.pval)
```

@@

## Explanation
